Structuring College Access

### 2025-04-18 index.qmd
included the results in the presentation
workin on discussion

```{r setup, echo=FALSE, results = 'asis', eval = FALSE}

@@

@@

- [YouVisit](https://www.youvisit.com/), 2019 -- virtual tours
- Cappex (now [appily](https://www.appily.com/)), 2020 -- college search engine
- Hobsons, 2021 -- edtech/consulting firm
  - PowerSchool buys Naviance; [EAB becomes exclusive reseller of Intersect](#){data-modal-type="image" data-modal-url="assets/images/intersect_connection_subscription_renewal_notice_university_utah_1_7_2022_redacted.png"}
    - (PowerSchool IPO in 2021; acquired by Bain Capital in 2024)
- [Concourse](https://discover.concourseglobal.net/student/start), 2022 -- direct admissions

@@

- Economics $\rightarrow$ effects of schools and policies (district/state/federal) on students
- Sociology $\rightarrow$ how schools and households sort students into colleges
  - Status attainment model [e.g., @RN915]
  - Cultural capital model [e.g., @RN1228; @RN4991]
  - Enrollment management behavior of colleges [e.g., @RN3519]

- Structural inequality $\rightarrow$ unequal student demand for college
  - Third-party products take snapshot student demand $\rightarrow$ encourage supply-side to amplify structural inequalities observed on demand-side
- Vendors have structured college access for decades [@RN5045]
  - Private equity + data science + software-as-service $\rightarrow$ financiers controlling process of sorting students to colleges
- Organizational field should be focus of regulation

>>>>

```{r setup, echo=FALSE, results = 'asis', eval = TRUE}

@@

<!-- - Economics $\rightarrow$ effects of schools and policies (district/state/federal) on students -->

__Sociology $\rightarrow$ how schools and households sort students into colleges__

- Demand-side explanations
  - Status attainment model [e.g., @RN915]
  - Cultural capital model [e.g., @RN1228; @RN4991]
- Supply-side explanations
  - The "credentialism" literature [e.g., @RN865; @RN861]
  - Enrollment management behavior of colleges [e.g., @RN3519]

- Structural inequality $\rightarrow$ unequal student demand for college
  - Third-party products take snapshot student demand $\rightarrow$ encourage supply-side to amplify structural inequalities observed on demand-side
- Vendors have structured college access for decades [@RN5045]
  - Private equity + data science + software-as-service $\rightarrow$ financiers control which students sorted to which colleges

@@

- [YouVisit](https://www.youvisit.com/), 2019 -- virtual tours
- [Cappex](https://www.appily.com/), 2020 -- college search engine
- Hobsons, 2021 -- edtech/consulting firm
  - PowerSchool buys Naviance; [EAB becomes exclusive reseller of Intersect](#){data-modal-type="image" data-modal-url="assets/images/intersect_connection_subscription_renewal_notice_university_utah_1_7_2022_redacted.png"}
    - (PowerSchool IPO in 2021; acquired by Bain Capital in 2024)
- [Concourse](https://discover.concourseglobal.net/student/start), 2022 -- direct admissions

@@
